---
title: "Untitled"
output: github_document
---
git commit -am 'date'
<!-- #git push origin +master -->

<!-- # https://github.com/satijalab/seurat/issues/1787 -->
<!-- # - merge just concatenates the counts or data table from two object together.  -->
<!-- # If either object has unique genes, it will be added in the merged objects. -->
<!-- #  -->
<!-- # - IntegrateData is a step in the integration, integrating two objects by anchor(matched biological state ('anchors')) cells.  -->
<!-- # - The detail you could find in the paper, here. -->
<!-- #  -->
<!-- # - You should only use merge for technical replicates, and in theory for a group of samples with a low batch effect.  -->
<!-- #  -->
<!-- # - Integration in Seurat (and related) was developed because there tends to be a relatively strong batch in the manifolds.  -->
<!-- # - By this I mean that even if two cell populations are the same between two samples,  -->
<!-- # - they will appear as two partially or fully separate clusters.  -->
<!-- # - Integration tries to "smooth out" the differences in batches so that cells that are likely similar will cluster together.  -->
<!-- # - As with anything single-cell related I would suggest exploring and validating the results from both merging and integration  -->
<!-- # to get a better feel for your data. -->
<!-- #  -->
<!-- # Merge samples into one Seurat object -->
<!-- # Make QC plots, split by sample. Merged object allows to easily examine different features on one plot -->
<!-- # Filter cells and genes, depending on batch structure (see below). -->
<!-- # Split merged object into samples again -->
<!-- # Integrate -->
<!-- # UMAP, clustering, etc. -->

<!-- # 1. Create all seurat objects. -->
<!-- # 2. Perform the quality-check and filtering for each one of them. -->
<!-- # 3. Calculate percent.mito. -->
<!-- # Normalize each dataset separately with SCTransform. Regress out percent.mito if desired. -->
<!-- # Calculate cell cycle scores. -->
<!-- # Prepare for integration with SelectIntegrationFeatures() and PrepSCTIntegration(). -->
<!-- # Integrate datasets. -->
<!-- # ScaleData, regressing out cell cycle score if desired -->
<!-- # Run PCA, UMAP, FindClusters, FindNeighbors on integrated assay. -->
<!-- # Switch to "SCT" assay and continue with the DE analysis. -->

<!-- #merge() conserved the original raw data of the objects; and IntegrateData() normalized the raw data? -->

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## GitHub Documents

This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.

## Including Code

You can include R code in the document as follows:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
