---
title: "Untitled"
output: github_document
---
git commit -am 'date'
git push origin +master 

## merge vs integration
https://github.com/satijalab/seurat/issues/1787 
- merge just concatenates the counts or data table from two object together.
- if either object has unique genes, it will be added in the merged objects. 
 
- IntegrateData is a step in the integration, integrating two objects by anchor(matched biological state ('anchors')) cells.  
- The detail you could find in the paper, here. 
- You should only use merge for technical replicates, and in theory for a group of samples with a low batch effect.  
- Integration in Seurat (and related) was developed because there tends to be a relatively strong batch in the manifolds.  
- By this I mean that even if two cell populations are the same between two samples,  
- they will appear as two partially or fully separate clusters.  
- Integration tries to "smooth out" the differences in batches so that cells that are likely similar will cluster together.  
- As with anything single-cell related I would suggest exploring and validating the results from both merging and integration  
to get a better feel for your data. 
 
## recomand pipeline
Merge samples into one Seurat object 
Make QC plots, split by sample. Merged object allows to easily examine different features on one plot 
Filter cells and genes, depending on batch structure (see below). 
Split merged object into samples again 
Integrate 
UMAP, clustering, etc. 

1. Create all seurat objects. 
2. Perform the quality-check and filtering for each one of them. 
3. Calculate percent.mito. 
Normalize each dataset separately with SCTransform. Regress out percent.mito if desired. 
Calculate cell cycle scores. 
Prepare for integration with SelectIntegrationFeatures() and PrepSCTIntegration(). 
Integrate datasets. 
ScaleData, regressing out cell cycle score if desired 
Run PCA, UMAP, FindClusters, FindNeighbors on integrated assay. 
Switch to "SCT" assay and continue with the DE analysis. 

##merge() conserved the original raw data of the objects; and IntegrateData() normalized the raw data? 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## path & package
```{r pressure, echo=TRUE}
q_dir = '/home/starjjbang/project/1_prof_kim_lab_deg/1_single_cell_project/'
fig_dir = paste0(q_dir, 'plot/7_0725_fig/',in_fod_dir)
rds_dir = paste0(q_dir, 'rds/4_220725/',in_fod_dir)
ref_dir = paste0(q_dir, 'result/5_0725_analysis/',in_fod_dir)
system(paste0('mkdir ',fig_dir))
system(paste0('mkdir ',rds_dir))
system(paste0('mkdir ',ref_dir))
source('/home/starjjbang/project/1_prof_kim_lab_deg/1_single_cell_project/code/single_function_ver02_0412.R')
```


